### 2023-04-03 application.tex
details

\section{Applications section}

@@

\begin{corollary}
{\sc resilience} is decidable for pushdown automata.
\end{corollary}

\begin{proof}
pushdown automata $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.

  \textcolor{red}{à faire Mathieu}
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} \alain{monotony ne semble pas strong...}avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.
\end{proof}
%
%
\subsection{LCM, VASS, semilinear VASS, Integer et Continuous VASS}

@@

se déduit du papier Schnoebelen RP 2010, page 8. RP is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}.

@@

\cite{DBLP:journals/ipl/BouajjaniEFMRWW00}

@@

>>>>

\section{Resilience in counter and fifo channel machines}

@@

\begin{theorem}
The three {\sc resilience} problems are decidable for pushdown automata with $\Safe$ and $\Bad$ regular languages.
\end{theorem}

\begin{proof}
Recall that resilience is equivalent to  $\Bad \subseteq \pred^*(\Safe)$. For every pushdown automaton $A=(Q,\Sigma,...)$ and every regular language $L \subseteq Q \times \Sigma^*$, the set $\pred^*(L)$ is a computable regular language \cite{DBLP:journals/ipl/BouajjaniEFMRWW00}
%
%			Moreover, $post^*(\Bad)$ is also a computable regular language \alain{pourquoi ?}   $post^*(L)$ and
so the inclusion $\Bad \subseteq \pred^*(\Safe)$ is decidable and resilience too.
%
BRP
%
kRP
%
\end{proof}
%
Let us remark that $\uparrow post^*(s)$ is also a computable regular language, but we cannot directly apply Theorem \ref{} since PA are not WSTS for the usual orderings.

%  \textcolor{red}{à faire Mathieu}
%Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} \alain{monotony ne semble pas strong...}avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.

%
%
\subsection{LCM, VASS, semilinear VASS, Integer et Continuous VASS}

@@

\begin{proof}
LCM se déduit du papier de Pachl (1986) that uses a regular inductive invariant to obtain a witness of non-reachability.

Schnoebelen RP 2010, page 8. RP is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of results in Section 3.4 of \cite{DBLP:conf/rp/Schnoebelen10}.

semilinear VASS

Integer et Continuous VASS
\end{proof}

@@

@@

Another proof is possible for LCS which have a (non-computable) regular reachability set. LCS are WSTS with a computable $\uparrow post^*(S)$.

### 2023-04-03 reachable-resilience.tex
up
details

\begin{proof}
Let $B_p$ be a basis of $\uparrow \post^*(s)$, $B_\Safe$ a basis of $\Safe$
and $\Bad$ decidable downward-closed.
By applying Lemma~\ref{Lemma intersection} twice, we obtain

$$ post^*(s) \cap \Bad \subseteq \pred^*(\Safe) \equiv B_p \cap \Bad \subseteq \pred^*(\Safe)$$

Since $B_p$ is finite and $\Bad$ is decidable, we can directly compute $ B_p \cap \Bad$.
% For every element of $ B_p \cap J$, checking that it is in $\pred^*(I)$ is the same as checking coverability of I, and thus decidable.
We can compute a basis of $\pred^*(\Safe)$ from $B_\Safe$, and hence check that $B_p \cap \Bad \setminus \pred^*(\Safe) = \emptyset$. 
\end{proof}

@@

However when removing strong compatibility, precision is lost.
Since $\pred(\uparrow \Safe)$ is not necessarily upward closed, it is possible to have 
 $\uparrow post^* (s) \cap S \not\subseteq \pred(\Safe)$,
despite having 
$post^* (s) \cap S \subseteq \pred( \Safe)$.
In such a case the algorithm from
\cite{DBLP:conf/gg/Ozkan22} would deduce that $1$-rechable-resilience does not hold,
which is incorrect.
An example of this is ...

>>>>

\begin{proof}
Let $B_s$ be a basis of $\uparrow \post^*(s)$, $B_\Safe$ a basis of $\Safe$
and $\Bad$ a downward-closed set given by its finite set of (maximal) ideals.
By applying Lemma~\ref{Lemma intersection} twice, we obtain

$$ post^*(s) \cap \Bad \subseteq \pred^*(\Safe) \equiv B_s \cap \Bad \subseteq \pred^*(\Safe)$$

Since $B_s$ is finite and $\Bad$ is decidable, we can directly compute $ B_s \cap \Bad$.
% For every element of $ B_p \cap J$, checking that it is in $\pred^*(I)$ is the same as checking coverability of I, and thus decidable.
We can compute a basis of $\pred^*(\Safe)$ from $B_\Safe$, and hence check that $B_s \cap \Bad \setminus \pred^*(\Safe) = \emptyset$. 
\end{proof}

@@

However when removing strong compatibility, precision is lost.
Since $\pred(\uparrow \Safe)$ is not necessarily upward-closed, it is possible to have 
 $\uparrow post^* (s) \cap S \not\subseteq \pred(\Safe)$,
despite having 
$post^* (s) \cap S \subseteq \pred( \Safe)$.
In such a case the algorithm from
\cite{DBLP:conf/gg/Ozkan22} would deduce that $1$-rechable-resilience does not hold,
which is incorrect.
% An example of this is ...
